### 2018-04-16 ident/docs/draft_2.tex
minor changes to results

	In corroboration of what we discussed in Section \ref{sec:example}, i.e., experiments must be able distinguish between different values of $v_1$ and acetate, the contribution of experiments that involve changes in the acetate concentrations, which consequently bring about changes in the value of $v_1$, contribute to a significant part (> 50\%) of the identifiable experimental data combinations in comparison to the other types of experiments (Figure \ref{fig:exp_info}a and b).

	For instance, identification of $V_1^{max}$ and $K_1^{ac}$ requires that the data from two different experiments used for parameter estimation must have distinct acetate concentrations as well as different uptake fluxes ($v_{1,j}$) between them (Equation \ref{eq:v1_par}). Thus, the informativeness of the experiments (changes in the input acetate concentration and $v_1$) for identifying parameters of $v_1$ is determined by the ability of the input change to effect a change in the measured value of $v_1$.	Since less than 50\% of all data combinations can satisfy these requirements, and can consequently identify $v_1$ (Figure \ref{fig:ident}a), we say that identifiability analysis is crucial to determine the minimum number of experiments, as well as the nature of experiments that can help identify parameters for $v_1$.

>>>>

	In corroboration of what we discussed in Section \ref{sec:example}, i.e., experiments must be able distinguish between different values of $v_1$ and acetate, the contribution of experiments that involve changes in the acetate concentrations, which consequently bring about changes in the value of $v_1$, contribute to a significant part (> 50\%) of the identifiable experimental data combinations in comparison to the other types of experiments (Figure \ref{fig:exp_info}a and b). Since less than 50\% of all data combinations can satisfy these requirements, and can consequently identify $v_1$ (Figure \ref{fig:ident}a), we say that identifiability analysis is crucial to determine the minimum number of experiments, as well as the nature of experiments that can help identify parameters for $v_1$.
